Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2018-01-12 PAPER.tex
Added text to describe the plot showing eigenvector convergence

\cc{Note to Adrian - somewhere in the next paragraph would be good to ref Fig17}
The resulting eigenspectrum as compared to the green curve (FG + EoR) in Figure \ref{fig:toy_sigloss2} is shown in Figure 
\ref{fig:toy_sigloss15}. The spectrum, in the case of fringe-rate filtering (dashed line), falls more steeply, especially for 
the last few eigenmodes. In many applications, this steep fall is not indicative of the true covariance structure of the data.

To quantify the convergence of `weak' and `strong' eigenmodes present in a sloped eigenspectrum, we form a mock covariance matrix with diagonal values that span $4$ orders of magnitude. We then draw random data realizations from this covariance and compute a convergence metric $\varepsilon(\widehat{\textbf{v}})$ for the empirical eigenvectors $\widehat{\textbf{v}}$:
\begin{equation}
\label{eq:converge_eig}
\varepsilon (\widehat{\textbf{v}}) \equiv \frac{1}{N_{f}}\sum_{i}^{N_{f}}|\textbf{v}-\widehat{\textbf{v}}|_{i},
\end{equation}
where $N_{f}$ is the number of frequencies ($20$) in the mock data. We plot this statistic against the number of realizations in Figure \ref{fig:toy_sigloss17}, which shows that...

@@

>>>>

The resulting eigenspectrum as compared to the green curve (FG + EoR) in Figure \ref{fig:toy_sigloss2} is shown in Figure 
\ref{fig:toy_sigloss15}. The spectrum, in the case of fringe-rate filtering (dashed line), falls more steeply, especially for 
the last few eigenmodes. In many applications, this steep fall is not indicative of the true covariance structure of the data.

@@

Just as important as the eigenvalues are the eigenvectors of our empirical covariances. In general, different eigenvectors converge to their true forms at different rates. This is illustrated by Figure \ref{fig:toy_sigloss17}, which shows the convergence of eigenvectors in an empirical estimate of a covariance matrix whose true form is a diagonal matrix with eigenvalues spanning four orders of magnitude. We use as a convergence metric $\varepsilon(\widehat{\textbf{v}})$ for the empirical eigenvectors $\widehat{\textbf{v}}$, defined as:
\begin{equation}
\label{eq:converge_eig}
\varepsilon (\widehat{\textbf{v}}) \equiv \sqrt{\sum_{i}^{N_{f}}|\textbf{v}-\widehat{\textbf{v}}|_{i}^2},
\end{equation}
where $N_{f}$ is the number of frequencies ($20$) in the mock data. The eigenmode convergence curves  in Figure \ref{fig:toy_sigloss17} are ranked ordered by eigenvalue, such that ``Eigenmode \# 1" illustrates the convergence of the eigenvector with the largest eigenvalue, ``Eigenmode \# 2" for the second largest eigenvalue, and so on. One sees that the stronger eigenmodes converge to their true eigenvectors more quickly. With only a small number of realizations, these empirically estimated modes already retain little correlation with the specific realizations of data that were used to form the empirical covariance. As we shall see in Section \acl{insert}, this minimizes signal loss. In contrast, the weaker eigenmodes retain more memory of the data realizations, which leads to correlations that induce signal loss. \acl{Think about whether we need to do the Fourier space version as well.}
